---
title: "Results"
---

::: {.section-badge}
Phase IV · The Analyst
:::

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(knitr)
library(kableExtra)

final <- readRDS("final_project_clean.RDS")
```

This section presents the findings of the content analysis (N = `r nrow(final)` items). Results are organized to address each research question in turn. Descriptive statistics are presented first, followed by inferential analysis.

---

## Descriptive Statistics

### Overview of the Sample

```{r}
#| label: tbl-sample-overview
#| tbl-cap: "Table 1. Sample composition by Gender."

final |>
  count(gender, name = "n") |>                    
  mutate(
    Percent = round(n / sum(n) * 100, 1),
    Percent = paste0(Percent, "%")
  ) |>
  rename(
    "Source / gender" = gender,                   
    "N" = n,
    "% of Sample" = Percent
  ) |>
  kable(align = c("l", "c", "c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

The sample was drawn from YouTube gameplay videos and using the gender variable as the main variable. By looking at the first moments of a video, specifically the character creation screen, it is shown what gender was chosen by the player. The largest share came from women, according for 49% of the total sample. Coverage was distributed unevenly across the study period, specifically with men and anyone who either chose they/them pronouns, gender-switching, or as gender performance was acted out. 

---

### Distribution of Primary Variable: Gender

```{r}
#| label: tbl-var1-freq
#| tbl-cap: "Table 2. Frequency distribution of Gender (N = 100, excluding code-9 items)."

final |>
  filter(gender != "Unable to Determine") |>        
  count(gender, name = "n") |>                      
  arrange(desc(n)) |>
  mutate(
    Percent = round(n / sum(n) * 100, 1),
    `Cumulative %` = round(cumsum(Percent), 1),
    Percent = paste0(Percent, "%"),
    `Cumulative %` = paste0(`Cumulative %`, "%")
  ) |>
  rename(
    "Gender" = gender,                   
    "N" = n
  ) |>
  kable(align = c("l", "c", "c", "c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

*(2–3 sentences describing Table 2. Report the most and least common categories. Connect to RQ1: does this distribution speak to what your first research question was asking?)*
Even though women were the dominant gender in the first table, the they came out as the least common category. The "other" identifier, including gender-switching or the use of they/them pronouns, came out on top with masculine right behind. This would say how different genders play cozy games, specifically how often they're being played and later showing the reasonings and the performance involved. 

---

### Bar Chart: Distribution of Gender

```{r}
#| label: fig-var1-bar
#| fig-cap: "Figure 1. Distribution of Gender across all coded items (N = 100, code-9 excluded). Those who identified as feminine were the highest in the dataset, with those identifying as masculine slightly under."
#| fig-width: 7
#| fig-height: 4.5

final |>
  filter(gender != "Unable to Determine") |>        
  count(gender) |>                                  
  mutate(
    pct = n / sum(n),
    gender = fct_reorder(gender, n, .desc = TRUE)     
  ) |>
  ggplot(aes(x = gender, y = pct, fill = gender)) +  
  geom_col(width = 0.65, show.legend = FALSE) +
  geom_text(
    aes(label = paste0(round(pct * 100, 1), "%")),
    vjust = -0.4,
    size = 3.5,
    color = "#333333"
  ) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0.08))
  ) +
  scale_fill_manual(values = c(
    "#b71c1c", "#e57373", "#ef9a9a", "#ffcdd2", "#880e4f"
  )) +
  labs(
    title = "Distribution of Gender",
    subtitle = "Source: YouTube, 04/01/2026-04/04/2026 | N = 100",
    x = "Gender",
    y = "Proportion of Items"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", color = "#b71c1c"),
    plot.subtitle = element_text(color = "#666666", size = 9),
    axis.title = element_text(color = "#333333"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```


The dominant category is feminine taking up nearly half of the dataset. It's fairly concentrated between masculine and feminine, with only 6% of people identifying with the "other" category. Most of the data will involve masculine presenting and feminine presenting people. 

---

### Distribution of Secondary Variable: Gaming Mechanics

```{r}
#| label: tbl-var2-freq
#| tbl-cap: "Table 3. Frequency distribution of Gaming Mechanics (N = 100, excluding code-9 items)."

final |>
  filter(gaming_mechanics != "Unable to Determine") |>        
  count(gaming_mechanics, name = "n") |>                      
  arrange(desc(n)) |>
  mutate(
    Percent = round(n / sum(n) * 100, 1),
    Percent = paste0(Percent, "%")
  ) |>
  rename(
    "Gaming Mechanics" = gaming_mechanics,                   
    "N" = n
  ) |>
  kable(align = c("l", "c", "c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

The gaming mechanic that was used the most often was the "community" mechanic, involving talking with NPC characters, gifting them, NPC quest completions, and donating to areas such as *Stardew Valley*'s Community Center and the museum in *Fields of Mistria*. The least common was the fishing mechanic in both games. This does align with the expected in the qualitative memo. 

---

## Inferential Analysis

### Chi-Square Test of Independence: Gender × Gaming Mechanics

```{r}
#| label: tbl-crosstab
#| tbl-cap: "Table 4. Cross-tabulation of Gender by Gaming Mechanic (N = 100, code-9 excluded)."

chi_data <- final |>
  filter(
    gender != "Unable to Determine",               
    gaming_mechanics != "Unable to Determine"                
  )

# Cross-tabulation table
cross_tab <- table(chi_data$gender, chi_data$gaming_mechanics)  

# Display as formatted table
cross_tab |>
  as.data.frame.matrix() |>
  rownames_to_column(var = "Gender") |>
  kable(align = "lcccc") |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 13
  ) |>
  add_header_above(
    c(" " = 1, "Gaming Mechanics" = ncol(cross_tab))  
  ) |>
  row_spec(0, bold = TRUE, background = "#b71c1c", color = "white")
```

Land and community were the most common in the table, with feminine being slightly higher when it came to the community tab. Surprisingly, romance and fishing remaining empty is the most surprising. Romance was shown throughout each player and their chosen NPC's, but this also ended up as part of the community interaction overall. Fishing is somewhat surprising, but players preferring land and community in comparison makes the most sense. Fishing is a challening mechanic in *Stardew Valley* and not as interesting to others in *Fields of Mistria*.

```{r}
#| label: chi-square-test
#| include: false

chi_result <- chisq.test(cross_tab)

chi_x2  <- round(chi_result$statistic, 2)
chi_df  <- chi_result$parameter
chi_p   <- round(chi_result$p.value, 3)
chi_sig <- ifelse(chi_result$p.value < .05,)

min_expected <- round(min(chi_result$expected), 2)
```

**Chi-Square Result:**

A Chi-Square test of independence was conducted to examine the relationship between Gender and Gaming Mechanic. The result was `NA`, χ²(`3.6039`) = `8`, *p* = `0.891`. It is not statistically significant. 
*Note: I had to use the `chisq.test(final$gender, final$gaming_mechanics)` to find values.*

A Chi-Square test of independence was conducted to examine the relationship between Gender and Gaming Mechanic. The result was `NA`, χ²(`10`) = `NaN`, *p* = `0.NaN`. It is not statistically significant. 

The chi_result$expected ran this:
             land mining community romance fishing undetermined
  other      2.16   0.72       2.4       0    0.12          0.6
  masculine 16.20   5.40      18.0       0    0.90          4.5
  feminine  17.64   5.88      19.6       0    0.98          4.9

```{r}
#| label: fig-mosaic
#| fig-cap: "Figure 2. Mosaic plot showing the relationship between Gender and Gaming Mechanic. Cell width represents the proportion of items in each Gaming category; cell height represents the proportion assigned each Gender value."
#| fig-width: 7
#| fig-height: 5

chi_data |>
  count(gender, gaming_mechanics) |>                           
  group_by(gaming_mechanics) |>                              
  mutate(prop = n / sum(n)) |>
  ggplot(aes(x = gaming_mechanics, y = prop, fill = gender)) + 
  geom_col(position = "fill", width = 0.7, color = "white", linewidth = 0.4) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c(
    "#b71c1c", "#e57373", "#ef9a9a", "#ffcdd2", "#880e4f"
  )) +
  labs(
    title = "Gender by Gaming Mechanic",
    subtitle = paste0(
      "χ²(", chi_df, ") = ", chi_x2, ", p = ", chi_p,
      " | Source: YouTube, 04/01/2026-04/05/2026"
    ),
    x = "Gaming Mechanic",
    y = "Proportion",
    fill = "Gender"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", color = "#b71c1c"),
    plot.subtitle = element_text(color = "#666666", size = 9),
    axis.text.x = element_text(angle = 25, hjust = 1),
    legend.position = "right"
  )
```

Based on the test ran through by both what was manually put in and previously ran, the results of the Chi-Square test are not statistically significant. This study did not provide a relationship between gender and gaming mechanic preferences overall, and returned more evened out results of gaming mechanics and gender identity. This also says that gender performance says little to none about gameplay videos as gameplay videos highlighted gaming mechanics, and gender would've only been performed if their gender identity coincided. At this time, the minumum expected cell count returned 0, though this may have been a conflict with initial coding overall. 

---

## Summary of Findings

- Feminine were the highest in the dataset with masculine slightly under.
- Overall gaming mechanics were evenly distribued through gender identity.

::: {.callout-note}
## Key Findings at a Glance

- **RQ1** Gameplay Videos and Gender: Feminine was 49% of the data while masculine was 46% and other at 6%. Between feminine and masculine, the gaming mechanics were evened out between land and community, with community being slightly higher with feminine than masculine. 

- **RQ2** Gender Performance and Gaming Mechanic Interactions: There was not a statistically significant finding between gaming mechanic and gender. 
:::
